Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
typo

The contributions of this paper are that:
%
{\em (i)}~We introduce \our, a new approach for building a sparse functional representation of a neural network.
{\em (ii)}~We demonstrate that, despite its sparsity, our method effectively captures predictive uncertainty, provides means of updating the model post-training, and gives a a compact regularizer suitable for continual learning.
{\em (iii)}~We provide extensive experiments for showcasing our approach and demonstrate significance and applicability across supervised, continual, and reinforcement learning, aiming to stimulate future use of the approach.

>>>>

The contributions of this paper are as follows:
%
{\em (i)}~We introduce \our, a new approach for building a sparse functional representation of a neural network.
{\em (ii)}~We demonstrate that, despite its sparsity, our method effectively captures predictive uncertainty, provides a means of updating the model post-training, and gives a compact regularizer suitable for continual learning.
{\em (iii)}~We provide extensive experiments for showcasing our approach and demonstrate significance and applicability across supervised, continual, and reinforcement learning, aiming to stimulate future use of the approach.
